---
title: "ToothGrowth Data Analysis"
author: "Christopher Jones"
date: "November 21, 2017"
output: pdf_document
---

In this report we examine ToothGrowth data, and draw some conclusions about it.

```{r setup, include=FALSE, tidy=TRUE, tidy.opts=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
read_chunk('StatInf1_PA1_ToothGrowth_Script.R')
```

## Data Loading 

We load and look at the general shape of the data here:

```{r load_external_code}
<<load>>
```

## Basic Summary & Data Analysis Of ToothGrowth Data

Basic summary statistics for the ToothGrowth dataset: 

```{r summary}
<<summary>>
```

And a visualization of how each supplement performs with dose/length:

```{r fdgdfcg}
<<ex_anal>>
```

## Tooth Growth Comparison By Supplement And Dose

We first use the t-test to compare the impact of supplement type on tooth growth:

```{r comparison_supp}
<<comparison1>>
```

Next we examine the impact of dosage on tooth growth

```{r comparison_dose}
<<comparison2>>
```


## Conclusions

Conclusions:

1. From the supplement test, we reject the hypothesis that the mean tooth growth differs according to the supplement. Supplement type by itself does not affect tooth length.
2. From the dosage tests we reject the hypothesis that mean tooth growth is by chance, and conclude that tooth length is affected (positively) by dosage level.


Assumptions:

1. The guinea pig populations are random and independent.
2. Sampled guinea pigs are representive of guinea pigs generally.
3. The variances between the compared populations are different.


